An Adolescent Mini-Neptune in the Kepler Field

### 2021-07-02 paper/ms.tex
update ttv slope units

\begin{figure*}[tp]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.9\textwidth]{f11.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
		{\bf Evidence for a prograde orbit from transit timing variations.}
    The time of each transit was measured, along with the local slope
    of the light curve.  The two quantities appear anti-correlated,
    which is most easily explained by starspot crossings during the
    first (second) half of transit inducing a positive (negative) TTV,
    provided that the orbit is prograde \citep{mazeh_time_2015}.
		\label{fig:ttvslope}
	}
\end{figure*}

@@

The precision of the Kepler data itself may enable more detailed
analyses without even needing to acquire more data.  While our transit
timing study did not yield the detection of any clearly significant
planet-induced TTVs, the star's flaring may be suggestive of
star-planet interactions.  Appendix~\ref{app:flare} highlights an odd flare
timing coincidence that may be worthy of further examination by those
more knowledgeable than us.

Ultimately however, our age measurement for \pn\ was enabled by
identifying its connection to the \cn\ using the Gaia data.  The
Supplementary Table~\ref{tab:v05} enables similar crossmatches to
already known planets, as well as forthcoming planets from the TESS
mission \citep{ricker_transiting_2015,guerrero_tess_2021}.  An
alternative approach also likely to bear fruit is to identify
kinematic associations around exoplanet host stars using the Gaia
data, and to then verify these associations with ancilliary rotation
periods and spectroscopy \citep{tofflemire_tess_2021}.

@@

L.G.B{.} and J.L.C{.} are grateful to T{.}~David for help with the
transit fitting, to R{.}~Kerr for kindly providing us with the
\citet{Kerr2021} membership list prior to its publication, and to
K.~Masuda for advice on gravity darkening.
% is grateful to G.~Zhou, B{.}~Tofflemire, A{.}~McWilliam,
% E{.}~Newton, M{.}~Kounkel, A{.}~Kraus, L{.}~Hillenbrand, and
% K{.}~Hawkins for the discussions on young stars, rotation, and lithium
% that encouraged this analysis.
%
L.G.B{.} acknowledges support by the TESS GI Program, programs
G011103 and G022117, through NASA grants 80NSSC19K0386 and
80NSSC19K1728.
%
L.G.B{.} was also supported by a Charlotte Elizabeth Procter
Fellowship from Princeton University.
%
This study was based in part on observations at Cerro Tololo
Inter-American Observatory at NSF's NOIRLab (NOIRLab Prop{.} ID
2020A-0146; 2020B-0029 PI: Bouma), which is managed by the
Association of Universities for Research in Astronomy (AURA) under a
cooperative agreement with the National Science Foundation.
%
% ACKNOWLEDGE PFS / CAMPANAS.
%
This paper also includes data collected by the TESS mission, which are
publicly available from the Mikulski Archive for Space Telescopes
(MAST).
%
Funding for the TESS mission is provided by NASA's Science Mission
directorate.
%
We thank the TESS Architects (G.~Ricker, R.~Vanderspek, D.~Latham,
S.~Seager, J.~Jenkins) and the many TESS team members for their
efforts to make the mission a continued success.
%

>>>>

\begin{figure*}[tp]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.9\textwidth]{f11.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
		{\bf Evidence for a prograde orbit from transit timing variations.}
    The time of each transit was measured, along with the local slope
    of the light curve.  The two quantities appear anti-correlated,
    which is most easily explained by starspot crossings during the
    first (second) half of transit inducing a positive (negative) TTV,
    provided that the orbit is prograde \citep{mazeh_time_2015}.  The
    units along the abscissa are most easily understood by considering
    that the flux from the star changes by $\sim$60\,ppt per half
    rotation period ($\sim$1.3\,days).
		\label{fig:ttvslope}
	}
\end{figure*}

@@

The precision of the Kepler data itself may enable more detailed
analyses without needing to acquire more data.  While our transit
timing study did not yield the detection of any clearly significant
planet-planet induced TTVs, the star's flaring may be suggestive of
star-planet interactions.  Appendix~\ref{app:flare} highlights an odd flare
timing coincidence that may be worthy of further examination by those
more knowledgeable than us.

Ultimately, our age measurement for \pn\ was enabled by identifying
its connection to the \cn\ using the Gaia data.  The Supplementary
Table~\ref{tab:v05} enables similar crossmatches to already known
planets, as well as forthcoming planets from the TESS mission
\citep{ricker_transiting_2015,guerrero_tess_2021}.  An alternative
approach would be to identify kinematic associations around exoplanet
host stars using the Gaia data, and to then verify these associations
with ancilliary rotation periods and spectroscopy
\citep{tofflemire_tess_2021}.

@@

L.G.B{.} and J.L.C{.} are grateful to T{.}~David for help with the
transit fitting, to R{.}~Kerr for kindly providing us with the
\citet{kerr_stars_2021} membership list prior to its publication.
% is grateful to G.~Zhou, B{.}~Tofflemire, A{.}~McWilliam,
% E{.}~Newton, M{.}~Kounkel, A{.}~Kraus, L{.}~Hillenbrand, and
% K{.}~Hawkins for the discussions on young stars, rotation, and lithium
% that encouraged this analysis.
%
L.G.B{.} acknowledges support by the TESS GI Program, programs
G011103 and G022117, through NASA grants 80NSSC19K0386 and
80NSSC19K1728.
%
L.G.B{.} was also supported by a Charlotte Elizabeth Procter
Fellowship from Princeton University.
%
This study was based in part on observations at Cerro Tololo
Inter-American Observatory at NSF's NOIRLab (NOIRLab Prop{.} ID
2020A-0146; 2020B-0029 PI: Bouma), which is managed by the
Association of Universities for Research in Astronomy (AURA) under a
cooperative agreement with the National Science Foundation.
%
% ACKNOWLEDGE PFS / CAMPANAS.
%
This paper also includes data collected by the TESS mission, which are
publicly available from the Mikulski Archive for Space Telescopes
(MAST).
%
Funding for the TESS mission is provided by NASA's Science Mission
directorate.
%
We thank the TESS Architects (G.~Ricker, R.~Vanderspek, D.~Latham,
S.~Seager, J.~Jenkins) and the many TESS team members for their
efforts to make the mission a continued success.
%
